Evaluation of classical correlation functions from 2/3D images on CPU and GPU architectures: introducing CorrelationFunctions.jl

### 2023-09-22 paper-correlations.tex
minor novelty

The aim of this paper is to establish a general open-source solution allowing to
compute all classical correlation functions. This solution should be well
documented with all computational algorithms explained, it should also leverage
on recent advances in programming high-intensity computations and utilize both
CPU and GPU power. Our answer in the form of \code{CorrelationFunctions.jl}
package allows to compute numerous CFs easily on any operating system. The
manuscript describing the package is organized as follows: in \cref{sec:math} we
introduce a reader to the most common and useful correlation functions,
\cref{sec:map} presents all algorithmic details for computing full CFs maps (map
method, full 2-point statistics for a given image). In \cref{sec:scan} we
discuss the second method to calculate correlation functions which is called the
scan approach. In \cref{sec:verification} we verify our algorithms based on
known analytical solutions. In \cref{sec:examples} some application examples are
provided, including CFs evaluation for multi-phase materials. Section
\ref{sec:efficiency} deals with computational efficiency of our code, we compare
computational times for 2D and 3D images of different sizes for scanning and map
methods as evaluated using either CPU or GPU.  Finally, sections
\ref{sec:outlook} and \ref{sec:summary} summarize all results and outline
possible future improvements.

>>>>

The aim of this paper is to establish a general open-source solution allowing to
compute all classical correlation functions. This solution should incorporate novel methods to compute CFs and be well
documented with all computational algorithms explained, it should also leverage
on recent advances in programming high-intensity computations and utilize both
CPU and GPU power. Our answer in the form of \code{CorrelationFunctions.jl}
package allows to compute numerous CFs easily on any operating system. The
manuscript describing the package is organized as follows: in \cref{sec:math} we
introduce a reader to the most common and useful correlation functions,
\cref{sec:map} presents all algorithmic details for computing full CFs maps (map
method, full 2-point statistics for a given image). In \cref{sec:scan} we
discuss the second method to calculate correlation functions which is called the
scan approach. In \cref{sec:verification} we verify our algorithms based on
known analytical solutions. In \cref{sec:examples} some application examples are
provided, including CFs evaluation for multi-phase materials. Section
\ref{sec:efficiency} deals with computational efficiency of our code, we compare
computational times for 2D and 3D images of different sizes for scanning and map
methods as evaluated using either CPU or GPU.  Finally, sections
\ref{sec:outlook} and \ref{sec:summary} summarize all results and outline
possible future improvements.
